More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-02-16 2016-Weak-FH-Bisim/WeakBisim.tex
Lotos laws

Strong bisim:\\
\centerline{hide \{g\} in a;B  ==  a; hide \{g\} in B  iff gatename(a)$\neq$g}\\
\centerline{hide \{g\} in a;B  ==  i; hide \{g\} in B  iff gatename(a)$=$g}

Weak congruence:\\
\centerline{a;i;B == a;B}\\
\centerline{B[]i;B == i;B}\\
and many others, often not easy to express without syntax for set operations.

>>>>

Strong bisim:\\
1) Hiding:\\
\centerline{hide \{g\} in a;B  ==  a; hide \{g\} in B  iff gatename(a)$\neq$g}\\
\centerline{hide \{g\} in a;B  ==  i; hide \{g\} in B  iff gatename(a)$=$g}
2) Disabling:\\
\centerline{B1[>(B2[>B3) == (B1[>B2)[>b3}\\
\centerline{(B1[>B2)[]B3 == B1[>B2}\\
\centerline{B[>stop == B}\\
\centerline{stop[>B == B}\\
\centerline{exit(...)[>B == exit(...)[]B}\\
3) Enabling:\\
\centerline{B1>>(B2>>B3) == (B1>>B2)>>b3}\\
\centerline{B>>stop == B|||stop}\\
\centerline{stop>>B == stop}\\
\centerline{exit>>B == i;B}\\
4) Choice:\\
\centerline{B1[](B2[]B3) == (B1[]B2)[]b3}\\
\centerline{B1[]B2 == B2[]B1}\\
\centerline{B[]stop == B}\\
\centerline{B[]B == B}\\

5) Others:\\
\centerline{B1|[]|B2 == B1|||B2}\\

Weak congruence:\\
\centerline{a;i;B == a;B}\\
\centerline{B[]i;B == i;B}\\
and many others, often not easy to express without syntax for set operations,
like e.g.:
\centerline{}
